Competing Bandits: The Perils of Exploration under Competition

### 2018-08-30 paper/content/model.tex
Added a footnote with regret rates.

Both \DEG and \TS are classic MAB algorithms, see \cite{Bubeck-survey12,TS-survey-FTML18} for background. It is well-known that \TS is near-optimal in terms of the cumulative rewards, and \DEG is very suboptimal, but still much better than \DG.%
\footnote{Precise formulations, namely upper/lower bound on \emph{regret} of the three algorithms, are not very relevant to this paper.} In a stylized formula:
    $ \TS \gg \DEG \gg \DG $
as stand-alone MAB algorithms.

>>>>

Both \DEG and \TS are classic MAB algorithms, see \cite{Bubeck-survey12,TS-survey-FTML18} for background. It is well-known that \TS is near-optimal in terms of the cumulative rewards, and \DEG is very suboptimal, but still much better than \DG.%
\footnote{Formally, \TS achieves regret 
    $\tilde{O}(\sqrt{TK})$ and
    $O(\tfrac{1}{\Delta} \log T)$,
where $\Delta$ is the gap in mean rewards between the best and second-best arms. \DEG has regret $\tilde{\Theta}(T^{2/3} K^{1/3})$ in the worst case. And \DG can have regret as high as $\Omega(T)$. Deeper discussion of these distinctions is not very relevant to this paper.}
In a stylized formula:
    $ \TS \gg \DEG \gg \DG $
as stand-alone MAB algorithms.
